Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2015-02-09 Article.tex
update

After a few increases in $ P^{MIN} $, the percentage of the random procedure starts dropping while it stays almost constant for our algorithm. For $ P^{MIN} = 8 $, we see that only a little more than half of the coalitions for the random case are able to enter while approximately $ 85 \%$ of them enters for the clique percolation algorithm. Finally, when the grid requirements become too high, the acceptance percentage of our algorithm tends slowly to zero (not shown in this plot for readability).

>>>>

After a few increases in $ P^{MIN} $, the percentage of the random procedure starts dropping while it stays almost constant for our algorithm. For $ P^{MIN} = 8 $, we see that $ 100 \% $ of the coalitions are able to enter with our algorithm while approximately $ 75 \%$ of them enters for the random case (only $40 \%$ and $15 \%$ for the other cases). Finally, when the grid requirements become too high, the acceptance percentage of our algorithm tends slowly to zero (not shown in this plot for readability).
